---
title: "Data_Science_Capstone_Wk4_Assignment"
author: "Choong-Hoon Hyun"
date: "2023-06-06"
output: html_document
---

### Load packages
```{r load packages, echo=TRUE}
library(tm)
library(stringr)
library(ngram)
library(ggplot2)
library(stringi)
```

### Download and unzip file 
```{r download files, echo=TRUE}
fileURL <- "https://d396qusza40orc.cloudfront.net/dsscapstone/dataset/Coursera-SwiftKey.zip"
f <- file.path(getwd(), "Coursera-SwiftKey.zip")
download.file(fileURL, f)

unzip(zipfile = "Coursera-SwiftKey.zip")
```

### Load the blogs, twitter, news data-set
```{r }
blogs_txt <- file("final/en_US/en_US.blogs.txt", open="r")
blogs <- readLines(blogs_txt, encoding = "UTF-8", skipNul = TRUE)
twitter_txt <- file("final/en_US/en_US.twitter.txt", open = "r")
twitters <- readLines(twitter_txt, encoding = "UTF-8", skipNul = TRUE)
news_text <- file("final/en_US/en_US.news.txt", open = "r")
news <- readLines(news_text, encoding = "UTF-8", skipNul = TRUE)
remove(blogs_txt) # Remove the file to free up the space in memory.
remove(twitter_txt) # Remove the file to free up the space in memory.
remove(news_text) # Remove the file to free up the space in memory.
```

### Clean the dataset
#### make all words to lowercase, remove stop-words, strip the punctuation, and strip numeric
```{r clean up, echo=TRUE}
cleanCorpus <- function(x) {
  myCorpus <- Corpus(VectorSource(x))
  myCorpus <- tm_map(myCorpus, PlainTextDocument)
  myCorpus <- tm_map(myCorpus, tolower)
  myCorpus <- tm_map(myCorpus, stripWhitespace)
  myCorpus <- tm_map(myCorpus, removeNumbers)
  myCorpus <- tm_map(myCorpus, removePunctuation)
  myCorpus <- tm_map(myCorpus, removeWords,stopwords("en"))
  myCorpus <- tm_map(myCorpus, stripWhitespace)
  myCorpus <- lapply(myCorpus, trimws)
  data.frame(sapply(myCorpus, as.character),stringsAsFactors = FALSE)
}

blog_clean <- cleanCorpus(blogs)
news_clean <- cleanCorpus(news)
twitter_clean <- cleanCorpus(twitters)
rm(blogs) # Remove the file to free up the space in memory.
rm(news) # Remove the file to free up the space in memory.
rm(twitters) # Remove the file to free up the space in memory.
``` 


### Merge each data-set
```{r merge, echo=TRUE}
lines_r <- rbind(blog_clean, news_clean, twitter_clean)
```

### Make 3-Grams dictionary
```{r 3-grams, echo=TRUE}
remove <- which(lines_r == "")
lines_r <- lines_r[-remove,]
```

### remove lines_r that contain less than 3 words, otherwise ngram() makes an error.
```{r remove lines_r, echo=TRUE}
lines_r <- lines_r[str_count(lines_r, "\\s+")>1]
trigrams <- ngram(lines_r, n = 3)
df_trigrams <- get.phrasetable(trigrams)
saveRDS(df_trigrams, "con_trigrams_final_project")
```

### Remove words of frequency of 1.
#### We remove the freuency of 1 words to improve the efficiency.
```{r remove freq 1, echo=TRUE}
df_notail <- df_trigrams[df_trigrams$freq > 1, ]
saveRDS(df_notail, "con_3gram_notail_en")
```

### Plot 3-grams of top 2,000 word frequency
#### We can confirm that the most frequent words are identical for both dataset.
```{r plot for 3-grams, echo =TRUE}
plot(df_trigrams[1:2000,]$freq, main = "3-grams word frequency (top 2,000)",
     xlab = "words", ylab = "Freuqency")

plot(df_notail[1:2000,]$freq, main = "3-grams word frequency without frequency of 1 (top 2,000)",
     xlab = "words", ylab = "Freuqency")
```

### Data-set comparision
#### 1. The file size is reduced to 25.5Mb from 446.1Mb.
#### 2. Size reduced dataset (df_notail) has 2704797 observation while 3-grams dataset (df_trigrams) has 42081542. It covers 6.427% of entries. 
#### 3. 3-grams dataset has total of 48326458 frequent words while "df_notail" data set has 8949713. "df_notail" dataset covers 18.5% instances.

### Conclusion
#### There are lots of entries of frequency of 1. We can achieve the efficiency.
```{r compare, echo=TRUE}
data.frame(File = c("3-grams", "3-grams_notail"),
           Size_Mb = c(round(file.info("con_trigrams_final_project")$size/1024^2, 1), 
                       round(file.info("con_3gram_notail_en")$size/1024^2, 1)), 
           Entries = c(nrow(df_trigrams), nrow(df_notail)), 
           frequency = c(sum(df_trigrams$freq), sum(df_notail$freq)))
```           

