---
title: 'CShiny Application and Reproducible Pitch'
date: "4 June 2023"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## How to use

Utilzing Galton Families dataset. We try to fit linear model to predict children height based on gender and parents height.

The application is running on https://r2po.shinyapps.io/course_project_shiny_appreproducible_pitch/

ui.R, and Server.R Code in my github repository https://github.com/drlang16/ShinnyApp-and-Reproducible-Pitch/upload/main

## Galton Families Dataset

Load data

```{r summary}
library(HistData)
data(GaltonFamilies)
summary(GaltonFamilies)
```

## Plot
Scatterplot is represented to display the prediction result
In the scatterplot below are represented the data used for the prediction model
```{r plot}
library(HistData)
data(GaltonFamilies)
plot(jitter(GaltonFamilies$childHeight) ~ GaltonFamilies$midparentHeight,xlab="Average Height of the Parents (in inches)",ylab="Height of the Child (in inches)",main="Scatterplot of Galton Family Data",pch=19,frame.plot=FALSE,col=ifelse(GaltonFamilies$gender=="female", "pink", "light blue"))
legend(65,80,pch=c(19,19),col=c("pink","light blue"),c("female", "male"),bty="o",cex=.8)
```

