---
title: "Data Science Capstone - Milestone Report"
output:
  html_document:
    df_print: paged
---

## Exploratory Analysis - SwiftKey

This report discusses about the training data set for SwiftKey for text prediction. It invloves the technique of exploratory analysis and the model is trained using a unified document corpus compiled from the three sources of three files which areen_US.twitter.txt, en_US.blog.txt, and en_US.news.txt. In each file, it contains text data from Twitter, blogs, and news articles, respectively. 

### Load library and data
```{r validation_data}
# load library knitr
library(knitr)

# blogs
blogs <- readLines(file("final/en_US/en_US.blogs.txt", open = "r"), 
                   encoding = "UTF-8", skipNul = TRUE)

# news
news <- readLines(file("final/en_US/en_US.news.txt", open = "r"), 
                  encoding = "UTF-8", skipNul = TRUE)

# twitter
twitter <- readLines(file("final/en_US/en_US.twitter.txt", open = "r"),
                     encoding = "UTF-8", skipNul = TRUE)
```

### Perform basic data summary:
Word counts, line counts and basic data tables.
```{r boosting}
library(stringi)
library(kableExtra)

# initialization of sample and file size
sampleSize = 0.01
fileSizeMB <- round(file.info(c("final/en_US/en_US.blogs.txt", 
                                "final/en_US/en_US.news.txt",
                                "final/en_US/en_US.twitter.txt"))$size / 1024 ^ 2)

# number of  lines, characters, words per file
numLines <- sapply(list(blogs, news, twitter), length)
numChars <- sapply(list(nchar(blogs), nchar(news), nchar(twitter)), sum)
numWords <- sapply(list(blogs, news, twitter), stri_stats_latex)[4,]

# words per line
wpl <- lapply(list(blogs, news, twitter), function(x) stri_count_words(x))

# words per line summary
wplSummary = sapply(list(blogs, news, twitter),
             function(x) summary(stri_count_words(x))[c('Min.', 'Mean', 'Max.')])
rownames(wplSummary) = c('WPL.Min', 'WPL.Mean', 'WPL.Max')

summary <- data.frame(
    File = c("en_US.blogs.txt", "en_US.news.txt", "en_US.twitter.txt"),
    FileSize = paste(fileSizeMB, " MB"),
    Lines = numLines,
    Characters = numChars,
    Words = numWords,
    t(rbind(round(wplSummary)))
)

kable(summary,
      row.names = FALSE,
      align = c("l", rep("r", 7)),
      caption = "") %>% kable_styling(position = "left",bootstrap_options = c("striped", "hover"))
```

### Histogram of WPL
```{r random_forest}
library(ggplot2)
library(gridExtra)
plot1 <- qplot(wpl[[1]],
               geom = "histogram",
               main = "US Blogs",
               xlab = "Words per Line",
               ylab = "Frequency",
               binwidth = 5)
plot1
```

```{r coloring plot}
plot2 <- qplot(wpl[[2]],
               geom = "histogram",
               main = "US News",
               xlab = "Words per Line",
               ylab = "Frequency",
               binwidth = 5)
plot2

plot3 <- qplot(wpl[[3]],
               geom = "histogram",
               main = "US Twitter",
               xlab = "Words per Line",
               ylab = "Frequency",
               binwidth = 1)
plot3
```